---
title: "overall_results"
author: "undina"
date: "2024-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(cowplot)
options(fig.height=6, fig.width=10)
```

```{r}
overall <- read_csv('results/agg_evals/overall_results_across_models.csv')
overall %>% head()
```
```{r}
overall %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method == 'lenient') %>% 
  group_by(base_name) %>%
  filter(macro_f1 == max(macro_f1))
```



```{r}
results <- overall %>%
  filter(ade_type == 'all', section == 'adverse reactions') %>% 
  group_by(base_name, eval_method) %>%
  filter(macro_f1 == max(macro_f1)) %>%
  ungroup() %>%
  pivot_longer(micro_precision:macro_f1, names_to = c('level', 'metric'),
               names_sep = '_', values_to = 'value')
# select(llm_model, level, metric, value)
results %>% head(20)
```


```{r, fig.height=6, fig.width=10}
results %>% filter(ade_type == 'all',
                   section == 'adverse reactions') %>%
  group_by(llm_model, eval_method, level, metric) %>% 
  summarize(mean_val = mean(value), 
            min_val = min(value),
            max_val = max(value),
           .groups = 'drop') %>%
  filter(level == 'macro',  eval_method == 'lenient') %>% 
  ggplot(mapping = aes(x = llm_model, y = mean_val, fill = llm_model,
                     ymin=min_val, ymax =max_val)) +
  geom_bar(stat = 'identity')  + #, position = 'dodge') +
  geom_errorbar(width = 0.4) +
  theme_cowplot() +
  theme(axis.text.x = element_blank()) + # element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle('Macro') +
  facet_wrap(~metric)
```


```{r,fig.height=6, fig.width=10}
results %>% filter(ade_type == 'all',
                   section == 'adverse reactions') %>%
  group_by(llm_model, eval_method, level, metric) %>%
  summarize(mean_val = mean(value), 
            min_val = min(value),
            max_val = max(value),
           .groups = 'drop') %>% 
  filter(level == 'micro', eval_method == 'lenient') %>%
ggplot(mapping = aes(x = llm_model, y = max_val, fill = llm_model)) +
                     # ymin=min_val, ymax =max_val)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  # geom_errorbar(width = 0.4) + 
  theme_cowplot() +
  theme(axis.text.x = element_blank()) + # element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle('Micro') +
  facet_wrap(~metric)

# ggsave('figures/embeds_performance.png', dpi = 1200,
#        width = 8, height = 4, bg = 'white')
```

# Granular results


```{r}
granular <- read_csv('results/agg_evals/granular_results_across_models.csv')
granular %>% distinct(llm_model)
```
```{r}
selected_gran_results <- granular %>%
  filter(section == 'adverse reactions',  # focus on ADR section
         ade_type == 'all', # not consider ade_type
         eval_method %in% c('ember-v1'), 
         llm_model != 'gpt-4-turbo-preview') %>%
  group_by(base_name, run) %>%
  mutate(mean_f1 = mean(f1, na.rm = T)) %>% ungroup() %>% group_by(base_name) %>%
  filter(mean_f1 == max(mean_f1)) %>% ungroup() %>% 
  pivot_longer(precision:f1, names_to = 'metric', values_to = 'value') %>%
  mutate(metric = metric %>%
           str_to_sentence,
         llm_model = llm_model %>%
           factor(.,ordered = T,
                  labels = c('exact', 'deepcadrme', 'code-llama-34b	',
                             'gpt-3.5-turbo-0125', 'gpt-4-1106-preview')) )
```

 precision = TP/(TP+FP)
        if TP == 0 and FN == 0:
            recall = np.NAN
        else:
            recall = TP/(TP+FN)
        if precision != 0 and recall != 0:
            f1 = (2 * precision * recall)/(precision + recall)# 2*TP/(2*TP+FP+FN)

```{r}
granular %>% 
  filter(section == 'adverse reactions',  # focus on ADR section
         ade_type == 'all', # not consider ade_type
         eval_method %in% c( 'lenient'), 
         llm_model != 'gpt-4-turbo-preview') %>%
  group_by(base_name, run) %>%
  mutate(mean_f1 = mean(f1, na.rm = T)) %>% ungroup() %>% group_by(base_name) %>%
  filter(mean_f1 == max(mean_f1)) %>% ungroup() %>% 
  group_by(llm_model) %>% 
  summarise(tot_tp = sum(tp),
            tot_fp = sum(fp),
            tot_fn = sum(fn),
            micro_precision = tot_tp/(tot_tp+tot_fp),
            micro_recall = tot_tp/(tot_tp+tot_fn),
            micro_f1 = 2*tot_tp/(2*tot_tp+tot_fp+tot_fn),
            macro_precision = mean(precision, na.rm = T),
            macro_recall = mean(recall, na.rm = T),
            macro_f1 = mean(f1, na.rm = T)) %>%
  select(-starts_with('tot')) %>% write_csv('results/agg_evals/agg_scores.csv')
  pivot_longer(micro_precision:macro_f1,
               names_sep = "_", names_to = c('level', 'metric'),
               values_to = 'value') %>%
  pivot_wider(names_from = level, values_from = value) %>%
  head
```



## Granular Box Plot Overall Performance

```{r}
selected_gran_results %>%
ggplot(mapping = aes(x = llm_model, y = value, color = llm_model, fill = llm_model)) +
  geom_jitter(alpha = 0.2) +
  geom_boxplot(colour = 'white') +
  facet_wrap(~metric) +
  theme_cowplot() +
  xlab('') +
  ylab('') + 
  # labs(fill = 'Model', color = 'Model') +
  scale_fill_manual(values=c("#3E0C48", "#33447D", "#00837F", "#44C15E", "#00A5F0")) + 
  scale_color_manual(values=c("#3E0C48", "#33447D", "#00837F", "#44C15E", "#00A5F0")) + # "#56B4E9")) + 
  theme(axis.text.x = element_blank(),
        strip.background = element_rect(fill="white"),
        legend.title = element_blank()) +
  panel_border()

ggsave('figures/granular_compare_extraction.png', dpi = 1200,
       width = 8, height = 4, bg = 'white')
```

## Granular Performance by Drug Label Length

## Plotting F1 score

### Get section character length

```{r}
section_length <- read_csv('data/section_char_count.csv')
section_length %>% head
```

### DeepCadreMe does not have results on training

```{r}

ann_text <- selected_gran_results %>%
  inner_join(section_length) %>%
  filter(!is.na(value)) %>%
  group_by(metric, llm_model) %>%
  summarise(label = str_glue('R = {signif(cor(value, num_char), digits = 2)}')) %>%
  ungroup() %>%
  mutate(x = 0.9,
         y = rep(c(0.05, 0.10, 0.15, 0.2), 3))

selected_gran_results %>%
  inner_join(section_length) %>%
ggplot(mapping = aes(x = num_char/1000, y = value, color = llm_model)) +
  geom_point(alpha = 0.35) +
theme_cowplot() +
  theme(legend.position = c(0.85,0.9),
        legend.title = element_blank(),
        strip.background=element_rect(colour="white",
                                      fill="white"),
        legend.box.background = element_rect(colour = "darkgray"),
        legend.text = element_text(
    margin = margin(r = 3, unit = "pt"))) +
  facet_wrap(~metric, nrow =  1) +
  xlab('Drug Label Character Length (in thousands)') +
  ylab('') +
  geom_text(data = ann_text, mapping = aes(x = x/1000, y = y, label = label),
            show.legend = FALSE) +
  geom_smooth(method = 'lm', se = F, show.legend = FALSE) +
  scale_color_manual(values=c("#3E0C48", "#00837F", "#44C15E", "#00A5F0")) + # "#56B4E9")) + 
  # scale_color_manual(values = c('#D81B60', '#1E88E5')) +
  ylim(c(0, 1))

# ggsave('figures/label_length_performance.png', dpi = 1200,
       # width = 7, height = 5, bg = 'white')
```

## Figure: Performance with Drug Label Length

```{r}
quantile_data <- selected_gran_results %>%
                  inner_join(section_length, by = c('drug_name', 'section')) %>%
                  filter(!is.na(value)) %>%
                  group_by(llm_model, metric) %>%
                  mutate(x_quantile = ntile(num_char, 15)) %>%
                  group_by(llm_model, metric, x_quantile) %>%
                  summarize(x_mean = mean(num_char),
                            y_mean = mean(value),
                            y_sd = sd(value),
                            y_min = y_mean - y_sd,
                            y_max = min(y_mean + y_sd, 1),
                            .groups = 'drop')

ann_text <- selected_gran_results %>%
  inner_join(section_length) %>%
  group_by(llm_model, metric) %>%
  summarise(label = str_glue('R = {signif(cor(value, num_char), digits = 2)}')) %>%
  ungroup() %>%
  mutate(x = 25,
         y = rep(c(0.05, 0.10, 0.15, 0.2), 3) - 0.05)

quantile_data %>%
ggplot(mapping = aes(x = x_mean/1000,
                     y = y_mean,
                     color = factor(llm_model))) +
  geom_point(alpha = 0.7) +
  geom_errorbar(aes(ymax = y_max,
                     ymin = y_min),
                alpha = 0.2) + 
  geom_smooth(method = 'lm', se = F, show.legend = FALSE) +
  geom_text(data = ann_text,
            mapping = aes(x = x, y = y, label = label),
            show.legend = FALSE) + 
  theme_cowplot() +
  theme(legend.title = element_blank(),
        strip.background=element_rect(colour="white",
                                      fill="white"),
        # legend.box.background = element_rect(colour = "darkgray"),
        axis.text = element_text(size = 10),
        legend.position =  'bottom', #c(0.75, 0.095),
        legend.text = element_text(size=10),
        legend.key.size = unit(0.5, "lines"),
        legend.margin=margin(c(1,3,3,1))) +
  scale_color_manual(values=c("#3E0C48", "#00837F", "#44C15E", "#00A5F0")) + # deepcadreme  "#33447D"
  facet_wrap(~metric, nrow =  1) +
  xlab('Drug Label Character Length (in thousands)') +
  ylab('') +
  panel_border() +
  ylim(c(0, 1)) 

ggsave('figures/granular_performance_label_length.png', dpi = 1200,
       width = 8, height = 4, bg = 'white')
```

## Figure: Performance by label length and ADE Type

```{r}
granular %>%
                filter(llm_model == 'gpt-4-1106-preview',
                       eval_method == 'lenient',
                       n_manual >= 3) %>% 
group_by(base_name, run) %>%
  mutate(mean_f1 = mean(f1, na.rm = T)) %>%
  ungroup() %>%
  filter(max(mean_f1) == mean_f1) %>% distinct(base_name, run)
                group_by(run, section) %>% 
                mutate(mean_f1 = mean(f1, na.rm=T)) %>%
                ungroup() %>%
                filter(max(mean_f1) == mean_f1) %>% distinct(base_name)
```


```{r}
ade_type_dat <- granular %>% 
                filter(llm_model == 'gpt-4-1106-preview',
                       eval_method == 'lenient',
                       n_manual >= 3) %>% 
                group_by(run, section) %>% 
                mutate(mean_f1 = mean(f1, na.rm=T)) %>%
                ungroup() %>%
                filter(max(mean_f1) == mean_f1) %>% 
                inner_join(section_length %>% 
                             filter(section == 'adverse reactions'),
                           by = c('drug_name', 'section')) %>% 
                mutate(ade_type = ade_type %>% str_to_title())

quant_ade_type <- ade_type_dat %>%
                  group_by(llm_model,ade_type) %>%
                  mutate(x_quantile = ntile(num_char, 15),
                         ade_type = str_glue('{ade_type} (N = {n()})')) %>%
                  group_by(llm_model,ade_type, x_quantile) %>%
                  summarize(x_mean = mean(num_char),
                            y_mean = mean(recall),
                            y_sd = sd(recall),
                            y_min = y_mean - y_sd,
                            y_max = min(y_mean + y_sd, 1),
                            .groups = 'drop')

quant_ade_type %>%
ggplot(mapping = aes(x = x_mean, y = y_mean, color = ade_type,
                     group = ade_type, linetype = ade_type)) +
  geom_point(position=position_dodge(width=0.5), alpha = 0.7) +
  geom_errorbar(aes(ymax = y_max,
                     ymin = y_min),
                alpha = 0.2,
                width = 0.1,
                position=position_dodge(width=0.5)) +
  geom_smooth(method = 'lm', se = F) +
  theme_cowplot() +
  theme(axis.text = element_text(size = 10),
        legend.position =  c(0.7, 0.12),
        legend.text = element_text(size=10),
        legend.title = element_blank(),
        legend.key.size = unit(0.5, "lines"),
        legend.box.background = element_rect(colour = "gray"),
        legend.margin=margin(c(1,3,3,1))) +
    guides(color = guide_legend(override.aes = list(size = 0.5))) +
  scale_color_manual(values = c('grey40', 'mediumpurple', 'aquamarine2', 'tomato2', 'royalblue')) +
  scale_linetype_manual(values = c('longdash', 'solid', 'solid', 'solid', 'solid'),
                 guide = F) +
  ylim(-0.05, 1) +
  ylab('Recall') +
  xlab('Drug Label Character Length') 

ggsave('figures/gpt-4_performance_ade-type.png', dpi = 1200,
       width = 6, height = 4, bg = 'white')
```





```{r, fig.height=8, fig.width=8}
granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview' , 'deepcadrme')) %>% 
  select(drug_name, f1, llm_model) %>%
  pivot_wider(names_from = llm_model, values_from = f1, values_fn = max)  %>%
  group_by(drug_name) %>% 
  mutate(gpt_better = `gpt-4-1106-preview` > deepcadrme) %>% 
  filter(!is.na(deepcadrme)) %>% 
ggplot(mapping = aes(x = `gpt-4-1106-preview`, y = deepcadrme,
                     # ymin = deep_min, ymax = deep_max,
                     color = gpt_better)) +
  geom_point(alpha = 0.5) + 
  scale_colour_discrete(guide = "none") +
  geom_abline() +
  theme_cowplot() +
  ylim(0.5,1) + xlim(0.5,1) + 
  theme(aspect.ratio = 1)
```


```{r, fig.width = 6, fig.height = 6}
granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview' , 'deepcadrme')) %>% 
  select(drug_name, precision, llm_model) %>%
  pivot_wider(names_from = llm_model, values_from = precision, values_fn = max)  %>%
  group_by(drug_name) %>% 
  mutate(gpt_better = `gpt-4-1106-preview` > deepcadrme) %>% 
  filter(!is.na(deepcadrme)) %>% 
ggplot(mapping = aes(x = `gpt-4-1106-preview`, y = deepcadrme,
                     color = gpt_better)) +
  geom_point(alpha = 0.5) + 
  scale_colour_discrete(guide = "none") +
  geom_abline() +
  theme_cowplot() +
  ylim(0.5,1) + xlim(0.5,1) + 
  theme(aspect.ratio = 1) +
  ggtitle('Precision')
```

```{r, fig.width = 6, fig.height = 6}
granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview' , 'deepcadrme')) %>% 
  select(drug_name, recall, llm_model) %>%
  pivot_wider(names_from = llm_model, values_from = recall, values_fn = max)  %>%
  group_by(drug_name) %>% 
  mutate(gpt_better = `gpt-4-1106-preview` > deepcadrme) %>% 
  filter(!is.na(deepcadrme)) %>% 
ggplot(mapping = aes(x = `gpt-4-1106-preview`, y = deepcadrme,
                     color = gpt_better)) +
  geom_point(alpha = 0.5) + 
  scale_colour_discrete(guide = "none") +
  geom_abline() +
  theme_cowplot() +
  ylim(0.5,1) + xlim(0.5,1) + 
  theme(aspect.ratio = 1) +
  ggtitle('Recall')
```


```{r}
granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview')) %>% 
ggplot(mapping = aes(x = drug_name, y = f1, color = drug_name)) +
  geom_point() +
  theme_cowplot() +
  scale_colour_discrete(guide = "none") +
  theme(axis.text.x = element_blank()) + 
  xlab('Drug')
```
```{r}
granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview')) %>% 
ggplot(mapping = aes(x = drug_name, y = recall, color = drug_name)) +
  geom_point(alpha = 0.5) +
  theme_cowplot() +
  scale_colour_discrete(guide = "none") +
  theme(axis.text.x = element_blank()) + 
  xlab('Drug')
```


```{r}
granular %>% 
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview')) %>%
  group_by(drug_name) %>%
  summarise(mean_val = mean(precision),
            min_val = min(precision),
            max_val = max(precision)) %>% ungroup() %>%
  arrange(mean_val)
ggplot(mapping = aes(x = drug_name, y = mean_val, color = drug_name,
                     ymin = min_val, ymax = max_val)) +
  geom_point(alpha = 0.5) +
  geom_errorbar() +
  theme_cowplot() +
  scale_colour_discrete(guide = "none") +
  theme(axis.text.x = element_blank()) + 
  xlab('Drug') +
  ylim(0,1)
```




```{r}
granular %>% 
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('deepcadrme'),
         run == '025') %>%
  group_by(drug_name) %>%
  summarise(mean_val = mean(precision),
            min_val = min(precision),
            max_val = max(precision)) %>% ungroup() %>% 
  arrange(mean_val)
ggplot(mapping = aes(x = drug_name, y = mean_val, color = drug_name,
                     ymin = min_val, ymax = max_val)) +
  geom_point(alpha = 0.5) +
  geom_errorbar() +
  theme_cowplot() +
  scale_colour_discrete(guide = "none") +
  theme(axis.text.x = element_blank()) + 
  xlab('Drug') +
  ylim(0,1)
```

```{r}
granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview')) %>% group_by(prompt, system, temp) %>%
  summarise(n())

granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview'),
         system %in% c('no-system-prompt','pharmexpert-v0')) %>% 
  select(drug_name, system, run, precision:f1) %>% head
  pivot_longer(precision:f1, names_to = 'metric', values_to = 'value') %>% 
  pivot_wider(names_from = system, values_from = value) %>% 
ggplot(mapping = aes(x = `no-system-prompt`, y = `pharmexpert-v0`)) +
  facet_wrap(~metric) +
  geom_point() + 
  theme_cowplot() +
  theme(aspect.ratio = 1) +
  labs(title = 'gpt-4-1106-preview_fatal-prompt-v2 -- System Prompt')
```

## Figure: Impact of Prompt on perfromance GPT 4

```{r, fig.height=6, fig.width=10}
granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview'),
         temp == 'temp0') %>% 
  select(drug_name, prompt, system, temp, precision:f1) %>%
  pivot_longer(precision:f1, names_to = 'metric') %>% 
  group_by(system, metric) %>%
  summarise(mean_val = mean(value), 
            min_val = min(value), 
            max_val = max(value), .groups = 'drop') %>% 
  # pivot_wider(names_from = system, values_from = mean_val,
  #             ymin = min_val, ymax = max_val) %>% head
ggplot(mapping = aes(x = system, y = mean_val,
                     ymin = min_val, ymax = max_val)) +
  geom_errorbar() + 
  geom_point() + 
  theme_cowplot() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~metric) +
  ylim(0,1) + 
  labs(title = 'different system prompts') 
```


```{r}
granular %>%
  filter(section == 'adverse reactions',
         ade_type == 'all',
         eval_method %in% c('lenient', 'test'),
         llm_model %in% c('gpt-4-1106-preview'),
         temp == 'temp0') %>% 
  select(drug_name, prompt, system, temp, precision:f1) %>%
  pivot_longer(precision:f1, names_to = 'metric') %>% 
  group_by(prompt, system, temp, metric) %>%
  summarise(mean_val = mean(value), 
            min_val = min(value), 
            max_val = max(value), .groups = 'drop') %>% 
  # pivot_wider(names_from = system, values_from = mean_val,
  #             ymin = min_val, ymax = max_val) %>% head
ggplot(mapping = aes(x = prompt, y = mean_val,
                     ymin = min_val, ymax = max_val, color = system)) +
  geom_errorbar(position=position_dodge(width=0.5)) + 
  geom_point(position=position_dodge(width=0.5)) + 
  theme_cowplot() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~metric) +
  ylim(0,1) + 
  labs(title = 'different system prompts') 
```

## Number of Tokens needed for Prompt + Response

```{r}
num_token_dat <- read_csv('data/num_tokens.csv') %>%
  pivot_longer(drug_label:response) %>%
  mutate(name = case_when(name == 'drug_label' ~ 'Drug Label',
                          name == 'response' ~ 'Extracted ADEs'))
xintercept = num_token_dat %>%
              distinct(name) %>%
              mutate(name = case_when(name == 'Drug Label' ~ 4096,
                          name == 'Extracted ADEs' ~ NA))
num_token_dat %>% head
```

```{r}
num_token_dat %>%
ggplot(mapping = aes(x = value, color = name, fill = name)) +
  geom_histogram(alpha = 0.7) + 
  geom_vline(aes(xintercept=intercept), color = 'red', linetype = 'dashed') +
  geom_vline(aes(xintercept=intercept - 1029),
             color = 'purple', linetype = 'dashed') +
  facet_wrap(~name, scales = 'free') +
  theme_cowplot() +
  theme(legend.position = '',
        strip.background = element_rect(fill="white")) +
  xlab('Number of Tokens') +
  ylab('Count') +
  panel_border()

ggsave('figures/num_tokens.png', dpi = 1200,
       width = 8, height = 4, bg = 'white')

```





